---
title: "centralDogma"
output: rmarkdown::pdf_document
editor: visual
vignette: >
  %\VignetteIndexEntry{centralDogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(centralDogma)
```

### INTRODUCTION

The library *centralDogma* provides different functions that allow the user to generate random DNA sequences, transcribe them, extract codons and generate base density plots, among others. The functions are below explained.

### FUNCTIONS

#### RANDOM_SEQ

#### TRANSCRIBE

This function uses a DNA sequence as input and returns its corresponding transcribed ARN by substituting "T" by "U". Example of use:

*transcribe("ACTG")* returns *"ACUG".*

#### GIVE_CODONS

#### INPUT_DNA

This function will enter a DNA triplette sequence and output the corresponding one-letter amino acid. Can also function with sequences of DNA, outputting several amino acids.

#### BASE_DENSITY
